Spatial Reasoning and Data Displays

### 2015-03-30 Paper/InfoVis2015/TestingVisualAptitude.Rnw
Caption fixes

Figure~\ref{fig:lineup} shows a sample lineup of boxplots; participants are expected to identify the most different among the plots shown. In this example, sub-plot 4 is the target  because of the noticeably different locations of the two boxplot medians.

@@

<<biplot-pca4, fig.cap="", fig.width=4.5, fig.height=4.5, warning=F, message=F, out.width='.45\\linewidth', comment="|", fig.cap="Biplots of principal components 1-4 with observations. Principal component analysis was performed on the four cognitive tests used to understand the association between the cognitive skills required for these tests and the skills required for the lineup protocol.  \\label{fig:biplots4}", echo=F, fig.env="figure">>=
#par(mar=c(4,4,.1,.1),cex.lab=.95,cex.axis=.9,mgp=c(2,.7,0),tcl=-.3)
dimnames(pca2$rotation)[[1]] <- c("card rotation", "figure classification", "paper folding", "visual search")

>>>>

Figure~\ref{fig:lineup}(a) shows a sample lineup of boxplots; participants are expected to identify the most different among the plots shown. In this example, sub-plot 4 is the target  because of the noticeably different locations of the two boxplot medians.

@@

<<biplot-pca4, fig.cap="", fig.width=4.5, fig.height=4.5, warning=F, message=F, out.width='.45\\linewidth', comment="|", fig.cap="Biplots of principal components 1-4 with observations (same as figure 1(b)). Principal component analysis was performed on the four cognitive tests used to understand the association between the cognitive skills required for these tests and the skills required for the lineup protocol.  \\label{fig:biplots4}", echo=F, fig.env="figure">>=
#par(mar=c(4,4,.1,.1),cex.lab=.95,cex.axis=.9,mgp=c(2,.7,0),tcl=-.3)
dimnames(pca2$rotation)[[1]] <- c("card rotation", "figure classification", "paper folding", "visual search")
